User guide to MSEtool

### 2018-08-03 inst/doc/MSEtool.Rmd
Update vignette intro

# Foreword

@@

* More data-rich assessment models
    * Virtual Population Analysis (VPA)
    * Age-Structure Production Models (ASPM)
    * Kalman filter assessment approximation

@@

# Introduction 
The MSEtool package is an extension of the DLMtool R package for implementing closed-loop simulation testing of management procedures, a process often referred to as management strategy evaluation (MSE). Whereas DLMtool is primarily designed for testing data-limited management procedures, MSEtool provides an object-oriented framework for creating data-rich management procedures (MPs), which typically involve combining an assessment model with a harvest control rule to provide a fishery management recommendation. MSEtool management procedures are designed to be used with the operating model of DLMtool through the `runMSE` function. The user guide to the DLMtool package is accessible via

@@

To facilitate a standardized design for data-rich MPs, MSEtool builds out the __MP__ class with constituent functions of class __Assess__ and __HCR__. An __MP__ can be made from these functions to be tested in a MSE within the DLMtool framework.

@@

_Figure 2: Design of MSEtool package for building management procedures from assessment models and harvest control rules for management strategy evaluations with the DLMtool package. Separate functions are also available for standardized reporting of output from assessment models in a stock assessment setting._

@@

>>>>

@@

* More data-rich assessment models
    * Virtual Population Analysis (VPA)
    * Kalman filter assessment approximation

@@

* Multi-stock and multi-fleet operating models

# Introduction 
MSEtool is an extension of the DLMtool package for implementing closed-loop simulation testing of management procedures, a process often referred to as management strategy evaluation (MSE). The components of the operating model for conducting MSEs for data-rich stocks is wholly contained within DLMtool, but MSEtool provides the tools for implementing additional features to facilitate such MSEs. Whereas DLMtool is primarily designed for testing data-limited management procedures, MSEtool provides an object-oriented framework for creating data-rich management procedures (MPs), which typically involve combining an assessment model with a harvest control rule to provide a fishery management recommendation. Management procedures created by MSEtool are designed to be used with the operating model of DLMtool through the `runMSE` function.

The user guide to the DLMtool package is accessible via

@@

@@

_Figure 2: Design of MSEtool package for building management procedures from assessment models and harvest control rules for management strategy evaluations with the DLMtool package. Assess and HCR functions and the Assessment object are unique to MSEtool, but work within the framework of DLMtool objects. Separate functions are also available for standardized reporting of output from assessment models in a stock assessment setting._

@@

# Acknowledgements
